---
title: "Dictionary"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 3
    #code_folding: hide
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

## List of Functions

### General bits

1. help(topic)-- pulls up the R documentation of the intended topic,should it exist

```{r}
help_run<- function(x){help(x)}
#topic must be entered in parenthesis to run function e.g. help_run("x")
help_run("mean")
help_run("ls")
```

2. ?topic-- similar to the help function, it pulls up the relavant R documentation of the intended topic, should it exist

```{r}
q_run<- function(x){?(x)}
#topic must be entered in parenthesis to run function e.g. q_run("x")
q_run("mean")
q_run("ls")
```

3. ls()-- returns a vector of the names of objects in the specified environment

```{r}
ls()
```

4. dir()-- returns the vector of the names of files or directories in a given directory

```{r}
dir_run<- function(x){dir(x)}
#topic must be entered in parenthesis to run function e.g. dir_run("x")
dir_run("Journal_files/figure-html")
```


5. list.files


### Input and Output
### Data Creation
### Slicing and Extracting Data
### Variable Conversion
### Variable Information
### Data Selection and Manipulation
### Math
### Matrices
### Advanced Data Processing
### Strings
### Plotting
### Distributions
### Programming