---
title: "Dictionary"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 3
    #code_folding: hide
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

## List of Functions

### General bits

1. help(topic)-- pulls up the R documentation of the intended topic,should it exist

```{r}
#help_run<- function(x){

  #return(help("x"))
#}

help("mean")
```

2. ?topic-- similar to the help function,  it pulls up the relavant R documentation of the intended topic, should it exist

```{r}

?mean
```

3. ls()-- returns a vector of the names of objects in the specified environment

```{r}
a<-ls()
print(a)
```

4. dir()
5. list.files


### Input and Output
### Data Creation
### Slicing and Extracting Data
### Variable Conversion
### Variable Information
### Data Selection and Manipulation
### Math
### Matrices
### Advanced Data Processing
### Strings
### Plotting
### Distributions
### Programming