---
title: "Dictionary"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 3
    #code_folding: hide
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

## List of Functions

### General bits

1. help(topic)-- pulls up the R documentation of the intended topic,should it exist

```{r}
help_run<- function(x){help(x)}
#topic must be entered in quotations to run function e.g. help_run("x")
help_run("mean")
help_run("ls")

help("mean")
```

2. ?topic-- similar to the help function, it pulls up the relavant R documentation of the intended topic, should it exist

```{r}
q_run<- function(x){?(x)}
#topic must be entered in quotations to run function e.g. q_run("x")
q_run("mean")
q_run("ls")

?mean
```

3. ls()-- returns a vector of the names of objects in the specified environment

```{r}
ls()

```

4. dir()-- returns the vector of the names of files or directories in a given directory

```{r}
dir_run<- function(x){dir(x)}
#directory must be entered in quotations to run function e.g. dir_run("x")
dir_run("Journal_files/figure-html")
#directory must be entered in quotations to run function e.g. dir_run("x")
dir_run(dir())

dir("Journal_files/figure-html")
```


5. list.files-- returns the vector of the names of files or directories in the named directory

```{r}
l_run<-function(x){list.files(x)}
#names of files or directories must be in quotations to run function e.g. l_run("x")
l_run("Journal_files")
#names of files or directories must be in quotations to run function e.g. l_run("x")
l_run(list.files())

list.files("Journal_files")
```

### Input and Output

1. save()
2. load()
3. data()
4. library()
5. read.table()
6. read.csv()
7. scan()
8. print()
9. cat()
10. write.table()

### Data Creation

1. c()
2. from:to(data_input)
3. seq()
4. rep()
5. data.frame()
6. list()
7. matrix()
8. factor()
9. rbind()
10. cbind()

### Slicing and Extracting Data
#### Indexing vectors

1. x[n] nth element
2. x[-n] all but nth element
3. x[1:n] first n elements
4. x[-(1:n)]elements from n+1 to the end
5. x[c(1,4,2)] specific elements
6. x["name"]
7. x[x>3] all elements greater 3
8. x[x>3 & x<5] all elements between 3 and 5
9. x[x %in% c("a","and","the")] all elements in given set

#### Indexing lists

1. x[n] list with elements n
2. x[[n]] nth element of the list
3. x[["name"]] elements of the list named "name"
4. x$name id


#### Indexing matrices

1. x[i,j] element at row i, column j
2. x[i,] row i
3. x[,j] column j
4. x[,c(1,3)] columns 1 and 3
5. x["name",] row named "name"

#### Indexing data frames (matrix indexing plus the following)

1. x[["name"]] column named "name"
2. x$nameid


### Variable Conversion

as.data.frame(x)
as.numeric(x)
as.logical(x)
as.character(x)

### Variable Information

is.na(x)
is.null(x)
is.data.frame(x)
is.numeric(x)
is.character(x)
length(x)
dim(x)
dimnames(x)
nrow(x)
ncol(x)
class()
attributes()

### Data Selection and Manipulation

which.max()
which.min()
which()
sort()
unique()
table()
sample()
### Math

### Math

max()
min()
range()
sum()
mean()
median()
var()
sd()
cor()
round()
abs()

### Matrices

t()
diag()
rowSums()
colSums()
rowMeans()
colMeans()

### Advanced Data Processing

apply()
aggregate()

### Strings

paste()
strsplit()
tolower()
toupper

### Plotting

hist()
plot()

### Distributions

rnorm()
runif()

### Programming
show that you can define a function
show that you can write a for loop
show that you can write a while loop
show that you can write an if else statement
Explain what return() does inside a function, show you can use it
Explain what break() does, show you can use it