---
title: "**Aira Contreras' Journal Adventure**"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 2
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```
# Harder Problems (1-11)

## Problem 11: Random Tic-Tac-Toe

2019 | Feb | 23 Last compiled: `r Sys.Date()`

##### Prompt: Imagine that two players make completely random choices when playing tic-tac-toe. Each game will either end in a draw or one of the two players will win. Create a monte-carlo simulation of this “random” version of tic-tac-toe. Out 10,000 simulations, what proportion of the time is the game won versus drawn?

##### Answer:

```{r}

```

## Problem 10: 99 Bottles of Beer Problem

2019 | Feb | 23 Last compiled: `r Sys.Date()`

##### Prompt: In this puzzle, write code to print out the entire “99 bottles of beer on the wall”" song. For those who do not know the song, the lyrics follow this form:

##### Answer:

```{r}
old_x<-0
new_x<-0
for (i in 99:1)
{
old_x<-i
new_x<-i-1
Sentence<-c(old_x,"bottles of beer on the wall",old_x,"bottles of beer Take one down, pass it around",new_x,"bottles of beer on the wall")
print(Sentence)
}

```

## Problem 9: 100 doors problem

2019 | Feb | 23 Last compiled: `r Sys.Date()`

##### Prompt: You have 100 doors in a row that are all initially closed. You make 100 passes by the doors. The first time through, you visit every door and toggle the door (if the door is closed, you open it; if it is open, you close it). The second time you only visit every 2nd door (door 2, 4, 6, etc.). The third time, every 3rd door (door 3, 6, 9, etc.), etc, until you only visit the 100th door.

##### Answer:

```{r}

```

## Problem 8: Monte Hall Problem

2019 | Feb | 23 Last compiled: `r Sys.Date()`

##### Prompt:A contestant in a game show is presented with three closed doors. They are told that a prize is behind one door, and two goats are behind the other two doors. They are asked to choose which door contains the prize. After making their choice the game show host opens one of the remaining two doors (not chosen by the contestant), and reveals a goat. There are now two door remaining. The contestant is asked if they would like to switch their choice to the other door, or keep their initial choice. The correct answer is that the participant should switch their initial choice, and choose the other door. This will increase their odds of winning

##### Answer:

```{r}

#doesn'tswitch

chancewin<-c()
win<-0
tries<-1:200
for (i in tries)
{
  curtains<-c(1,0,0)
  choice<-sample(curtains,1)
  #print(choice)
  chancewin<-c(chancewin,choice)
  #print(chancewin)
  win<-win+choice
  #print(win)
}
sum(chancewin)/length(chancewin)
win/length(tries)

#switches
switchs<-0
chances<-1:200

for(i in chances)
{
  curtains<-c(1,0,0)
  choice<-sample(curtains,3)
  if(choice[2]==0)
  {
    finchoice<-choice[1]+choice[3]
  }
  else
  {
    finchoice<-choice[1]+choice[2]
  }
  switchs<-switchs+finchoice
}
print(switchs)
switchs/length(chances)
```
## Problem 7: Dice-rolling simulations

2019 | Feb | 23 Last compiled: `r Sys.Date()`

##### Prompt:Assume that a pair of dice are rolled. Using monte carlo-simulation, compute the probabilities of rolling a 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, and 12, respectively.

##### Answer:

```{r}
die1<-sample(c(1,2,3,4,5,6),1)
die2<-sample(c(1,2,3,4,5,6),1)
rolldice<-function()
{
roll<-die1+die2
return(roll)
}
rolldice()
```


## Problem 6: Snakes and Ladders

2019 | Feb | 23 Last compiled: `r Sys.Date()`

##### Prompt:Your task here is to write an algorithm that can simulate playing the above depicted Snakes and Ladders board.

##### Answer:
```{r}

SnakesLadders<-function()
{
die<-sample(c(1,2,3,4,5,6),1)
#print(die)

ladders<-data.frame(start=c(1,4,9,21,28,36,51,71,80),end=c(37,14,31,42,84,44,67,91,100))


slides<-data.frame(start=c(98,95,93,87,64,62,56,49,47,16), end=c(78,75,73,24,60,19,53,11,26,6))

#print(ladders)
#print(slides)

loc<-0
nroll<-0
slide<-0
ladder<-0


  die
  loc<-loc+die
  nroll<-nroll+1
  
    if(any(ladders$start %in% loc))
    {
      loc<-ladders$end[ladders$start %in% loc]
      ladder<- ladder +1
    }
  
    if(any(slides$start %in% loc))
    {
      loc<-slides$end[slides$start %in% loc]
      slide<-slide+1
    }
  

  
  return(loc)
}

SnakesLadders()

```


## Problem 5: Encrypt and Decrypt the Alphabet

2019 | Feb | 23 Last compiled: `r Sys.Date()`

##### Prompt:Turn any normal english text into an encrypted version of the text, and be able to turn any decrypted text back into normal english text. A simple encryption would be to scramble the alphabet such that each letter corresponds to a new randomly chosen (but unique) letter.

##### Answer:

```{r}
alp<-"abcdefghijklmnopqrstuvwxyz"
alph<-strsplit(alp,"")[[1]]
#print(alph)
scralph<-sample(alph)
#print(scralph)
encrypkey<-data.frame(alph,scralph)
#print(encrypkey[,3])

encryption<-function(input,key)
{
  enc_alph<-c()
for(i in 1:length(input))
  {
  o_alph<-input[i]
  #print(o_alph)
  n_alph <- as.character(key[key$alph==o_alph,]$scralph)
  #print(c(o_alph, n_alph))
  enc_alph[i]<-n_alph
  #print(enc_alph)
  }
    return(enc_alph)
}


deencryption<-function(input,key)
{
  denc_alph<-c()
  for(i in 1:length(input))
  {
    c_alph<-input[i]
    d_alph<-as.character(key[key$scralph==c_alph,]$alph)
    denc_alph[i]<-d_alph
  }
  return(denc_alph)
}

code<-encryption(alph,encrypkey)
print(code)
deencryption(code,encrypkey)

```


## Problem 4: Multiplication Table

2019 | Feb | 23 Last compiled: `r Sys.Date()`

##### Prompt:Generate a matrix for a multiplication table.

##### Answer:

```{r}
r<-1:10
names(r)<-r
a<-r%o%r
print(a)

matrix(a,ncol = 10,nrow = 10)
```


## Problem 3: Test the Random Number Generator

2019 | Feb | 23 Last compiled: `r Sys.Date()`

##### Prompt: Test the random number generator for a flat distribution. Generate a few million random numbers between 0 and 100. Count the number of 0s, 1s, 2s, 3s, etc. all the way up to 100. Look at the counts for each of the numbers and determine if they are relatively equal.

##### Answer:

```{r}
a<-floor(runif(100,min=0,max=100))
hist(a)
b<-sort(unique(a))
#print(b)
c<-unlist(list(rep(0,length(b))))
#print(c)

for(i in a)
{
d<-match(i,b)
c[d]=c[d]+1
}
#print(c)
for(i in 1:length(b))
{
  print.table(c(b[i],c[i]))
}

g<-runif(10^6,min=0,max=100)
hist(g)


```


## Problem 2: Frequency Counts

2019 | Feb | 23 Last compiled: `r Sys.Date()`

##### Prompt: Take text as input, and be able to produce a table that shows the counts for each character in the text. This problem is related to the earlier easy problem asking you to count the number of times that a single letter appears in a text. The slightly harder problem is the more general version: count the frequencies of all unique characters in a text.

##### Answer:

```{r}
a<-"all you need to do is completely make an ass of yourself and laugh it off to realise that life is not so bad after all."
b<-unlist(strsplit(a,split = ""))
#print(b)
c<-unique(b)
#print(c)
d<-unlist(list(rep(0,length(c))))
#print(length(d))
for(i in b)
{
e<-match(i,c)

d[e]=d[e]+1

}
#print(d)
#print(c)

for (i in 1:length(c))
{
  print(c(c[i],d[i]))
}

```

## Problem 1: FizzBuzz Problem

2019 | Feb | 23 Last compiled: `r Sys.Date()`

##### Prompt: List the numbers from 1 to 100 with the following constraints. If the number can be divided by three evenly, then print Fizz instead of the number. If the number can be divided by five evenly, then print Buzz instead of the number. Finally, if the number can be divided by three and five evenly, then print FizzBuzz instead of the number. 

##### Answer:

```{r}
a<-seq(1,100,1)

for (i in a) 
{
  
  if(i%%3==0 & i%%5==0)
  {
    i<-"FizzBuzz"
    print(i)
  }
  else if(i%%5==0)
  {
   i<-"Buzz"
   print(i)
  }
  else if(i%%3==0)
  {
    i<-"Fizz"
    print(i)
  }
  else if(i)
  {
    print(i)
  }
}

```


# Easy Problems (1-21)

## Problem 21: Table it!

2019 | Feb | 23 Last compiled: `r Sys.Date()`

##### Prompt: Output any matrix to a txt file using commas or tabs to separate column values, and new lines to separate row values

##### Answer:

```{r}
here<-matrix(floor(runif(100, min = 1,max = 100)),nrow = 20,ncol = 20)
tmpfil<-tempfile("data")
write.table(here,tmpfil)
read.table(tmpfil)

here2<-matrix(floor(runif(100, min = 1,max = 100)),nrow = 20,ncol = 20)
tmpfil2<-tempfile("data")
write.csv(here2,tmpfil2,row.names = FALSE,col.names = F)
read.csv(tmpfil2)
```


## Problem 20: Table it?

2019 | Feb | 23 Last compiled: `r Sys.Date()`

##### Prompt: Create a variable that stores a 20x20 matrix of random numbers

##### Answer:

```{r}
here<-matrix(floor(runif(100, min = 1,max = 100)),nrow = 20,ncol = 20)
print(here)
```


## Problem 19: Write it out

2019 | Feb | 23 Last compiled: `r Sys.Date()`

##### Prompt: Output the contents of a variable to a .txt file

##### Answer:

```{r}
x<-matrix(1:10, ncol = 5)
fil<-tempfile("data")
write(x,fil)
read.csv(fil)
```

## Problem 18: Read Me!

2019 | Feb | 23 Last compiled: `r Sys.Date()`

##### Prompt: Read a .txt file or .csv file into a variable

##### Answer:
```{r}
tfile<-read.delim("http://www.sthda.com/upload/boxplot_format.txt")

t2file<-read.delim("https://www.w3schools.com/tags/tag_input.asp")

head(tfile)
head(t2file)
```

## Problem 17: Time it!

2019 | Feb | 23 Last compiled: `r Sys.Date()`

##### Prompt: Measure how long a piece of code takes to run by measuring the time before the code is run, and after the code is run, and taking the difference to find the total time

##### Answer:

```{r}
t1<-Sys.time()
a<-"The sky is clear; the stars are twinkling.
She always speaks to him in a loud voice.
The book is in front of the table.
I would have gotten the promotion, but my attendance wasn’t good enough.
If you like tuna and tomato sauce- try combining the two. It’s really not as bad as it sounds."
b<-unlist(strsplit(a,split = "e"))
length(b)-1
t2<-Sys.time()
runtime<-t2-t1
print(runtime)

```

## Problem 16: Do you have the time?

2019 | Feb | 23 Last compiled: `r Sys.Date()`

##### Prompt: Put the current computer time in milliseconds into a variable

##### Answer:
```{r}
curr.time<-(as.numeric(Sys.time()))*1000
print(curr.time,digits=15)
```

## Problem 15: Are you here, "here"?

2019 | Feb | 19 Last compiled: `r Sys.Date()`

##### Prompt: Do a logical test to see if one word is found within the text of another string variable.

##### Answer:

```{r}
a<-"I was very proud of my nickname throughout high school but today- I couldn’t be any different to what my nickname was."
c<-unlist(strsplit(a,split = " "))
b<-"nickname"
b%in%c
b%in%a #not sure why this doesn't work yet...

test_word <- "hello"
test_sentence <-"is the word hello in this sentence"
test_word%in%test_sentence #Shouldershrugs
```

## Problem 14: Why so many e's?

2019 | Feb | 19 Last compiled: `r Sys.Date()`

##### Prompt: Count the number of times a specific character occurs in a string variable

##### Answer:
```{r}
a<-"The sky is clear; the stars are twinkling.
She always speaks to him in a loud voice.
The book is in front of the table.
I would have gotten the promotion, but my attendance wasn’t good enough.
If you like tuna and tomato sauce- try combining the two. It’s really not as bad as it sounds."
b<-unlist(strsplit(a,split = "e"))
print(b)
length(b)-1
```


## Problem 13: Enough Sentences?

2019 | Feb | 19 Last compiled: `r Sys.Date()`

##### Prompt: Count the number of sentences in a string variable

##### Answer:
```{r}
a<-"Christmas is coming.
I want to buy a onesie… but know it won’t suit me.
She borrowed the book from him many years ago and hasn't yet returned it.
If the Easter Bunny and the Tooth Fairy had babies would they take your teeth and leave chocolate for you?
Check back tomorrow; I will see if the book has arrived.
Cats are good pets, for they are clean and are not noisy.
This is the last random sentence I will be writing and I am going to stop mid-sent
We have never been to Asia, nor have we visited Africa.
The river stole the gods.
She always speaks to him in a loud voice."
b<-unlist(strsplit(a,split = "[.?]"))
print(b)
length(b)
```


## Problem 12: WORD COUNT!

2019 | Feb | 19 Last compiled: `r Sys.Date()`

##### Prompt: Count the number of words in a string variable

##### Answer:
```{r}
a<-"Writing a list of random sentences is harder than I initially thought it would be."
b<-unlist(strsplit(a,split = " "))
length(b)

```


## Problem 11: You used how many letters?

2019 | Feb | 19 Last compiled: `r Sys.Date()`

##### Prompt: Count the number of characters in a string variable

##### Answer:
```{r}
a<-"adskfjhkadsjfh"
b<-unlist(strsplit(a,split = ""))
print(b)
length(b)

```


## Problem 10: Functions:Mean,Median,Mode,Range,St.dev

2019 | Feb | 19 Last compiled: `r Sys.Date()`

##### Prompt: Write your own functions to give descriptive statistics for a vector variable storing multiple numbers. Write functions for the following without using R intrinsics: mean, mode, median, range, standard deviation

##### Mean Answer:
```{r}
my_mean<-function(x)
{
  return(sum(x)/length(x))
  
}
t<-c(1:20)
my_mean(t)
```
##### Mode Answer:
```{r}
my_mode<-function(x)
{
 a<-sort(x)
  b<-unique(a)
  maxn<-0
  countn<-0
  for (i in b)
  {
  c<-a[a==i]
  if(length(c)>countn)
    {
    maxn=i
    countn=length(c)
    }
  }
 return(maxn)
}

my_mode(c(1,1,1,10,9,8,8,5,5,5,5))
```
##### Median Answer:
```{r}

my_median<-function(x)
{
  a<-sort(x)
  b<-length(x)
  c<-floor(b/2)
  if(b%%2==0)
  {
    return(mean(c(a[c],a[c+1])))
    
  }
  else
  {
   return(a[c+1])   
  }
}

my_median(c(1,2,3,4,5))
my_median(1:10)
```
##### Range Answer:
```{r}
my_range<-function(x)
{
  sort(x)
  print(c(min(x),max(x)))
}

my_range(c(1,1,1,10,9,8,8,5,5,5,5))
```
##### Standard Deviation Answer:
```{r}

my_sd<-function(x)
{
  avgx<-mean(x)
  sd<-0
  for (i in x)
  {
    sd<-(i-avgx)^2 + sd
  }
  return(sqrt(sd/(length(x)-1)))
}
my_sd(c(-5,1,8,7,2))
```
## Problem 9: 1:100 only if...

2019 | Feb | 19 Last compiled: `r Sys.Date()`

##### Prompt: Generate 100 random numbers within a specific range

##### Answer:

```{r}
#prints all numbers
runif(100, min = 1,max = 100)

#prints integers
floor(runif(100, min = 1,max = 100))

```
## Problem 8: Random One Hundred

2019 | Feb | 19 Last compiled: `r Sys.Date()`

##### Prompt: Generate 100 random numbers

##### Answer:
```{r}
#prints all numbers
runif(100)

```


## Problem 7: Where my Primes At?

2019 | Feb | 19 Last compiled: `r Sys.Date()`

##### Prompt: List all of the prime numbers from 1 to 1000

##### Answer:
```{r}
prime<-function(x,y)
{
  a<-seq(x,y,1)
  for(i in a)
  {
    c<-"Prime"
    if(i<=1){ c<-"Not Prime"}
    if (i>3)
    {
      
      b<-floor(sqrt(i))
      for(j in 2:b)
      {
        
        if(i%%j==0)
        {
          c<-"Not Prime"
        }
      }
      
    }
    if(c=="Prime")
      {
      print(c(c,i))
      }
  }
}
prime(1,1000)
```

## Problem 6: Odd Numbers Say What?


2019 | Feb | 19 Last compiled: `r Sys.Date()`

##### Prompt: List all of the odd numbers from 1 to 100

##### Answer:

```{r}
seq(1,100,2)

a<-1:100
for (i in a)
{
  if (i%%2!=0)
  {
    print(i)
  }
}
```


## Problem 5: Sum w. Functions

2019 | Feb | 19 Last compiled: `r Sys.Date()`

##### Prompt: Write a function to find the sum of all integers between any two values

##### Answer:
Sum of All Integers(Random) Sol:
```{r}
rsum<-function(x,y){return(sum(seq(x,y,1)))}

rsum(1,2)
rsum(1,10)
```

## Problem 4: Find the Sum!

2019 | Jan | 30 Last compiled: `r Sys.Date()`

##### Prompt: Find the sum of all integers from 1 to 100

##### Answer:
sum function Sol:
```{r}
a<-c()
for(i in 1:100) {
  a<-c(a,i)
}
print(a)
b<-sum(a)
print(b)
```
Loop Sol:
```{r}
c<-0
for(i in 1:100) {
  c<-c+i
}
print(c)
```


## Problem 3: 1:100, Loop, Sequence

2019 | Jan | 29 Last compiled: `r Sys.Date()`

##### Prompt: Write code that will place the numbers 1 to 100 separately into a variable using for loop. Then, again using the seq function.

##### Answers:

Loop Sol. #1:
```{r}
Alex<-c()

for (i in 1:100) {
  Alex<-c(Alex,i)
  }

print(Alex)
```

Loop Sol. #2:
```{r}
Sol2<-seq(1,100,1)

print(Sol2)
```


## Problem 2: Simple Math w. Variables

2019 | Jan | 29 Last compiled: `r Sys.Date()`

##### Prompt: Put numbers into variables, do simple math on the variables

##### Answers:
Variable Assingment:
```{r}
A<-5
B<-10
C<-25
D<-30
```
Addition:
```{r}
A+D
```
Subtraction:
```{r}
D-C
```
Multiplication:
```{r}
D*A
```
Division:
```{r}
C/A
```

## Problem 1: Simple Math

2019 | Jan | 29  Last compiled: `r Sys.Date()`

##### Prompt: Do simple math with numbers, addition, subtraction, multiplication, division

##### Answers:
Addition
```{r}
29+20
```
Subtraction
```{r}
29-18
```
Multiplication
```{r}
8*8
```
Division
```{r}
37/5
```


