---
title: "Aira Contreras' Journal Adventure"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```
# Problem 3: Prompt and Answer

2019 | Jan | 29 Last compiled: `r Sys.Date()`

##### Prompt: Write code that will place the numbers 1 to 100 separately into a variable using for loop. Then, again using the seq function.

##### Answers:

Loop Sol. #1:
```{r}
Alex<-c()

for (i in 1:100) {
  Alex<-c(Alex,i)
  }

print(Alex)
```

Loop Sol. #2:
```{r}
Sol2<-seq(1,100,1)

print(Sol2)
```


# Problem 2: Prompt and Answer

2019 | Jan | 29 Last compiled: `r Sys.Date()`

##### Prompt: Put numbers into variables, do simple math on the variables

##### Answers:
Variable Assingment:
```{r}
A<-5
B<-10
C<-25
D<-30
```
Addition:
```{r}
A+D
```
Subtraction:
```{r}
D-C
```
Multiplication:
```{r}
D*A
```
Division:
```{r}
C/A
```

# Problem 1: Prompt and Answer

2019 | Jan | 29  Last compiled: `r Sys.Date()`

##### Prompt: Do simple math with numbers, addition, subtraction, multiplication, division

##### Answers:
Addition
```{r}
29+20
```
Subtraction
```{r}
29-18
```
Multiplication
```{r}
8*8
```
Division
```{r}
37/5
```

# The big idea

Use this lab journal to record what you do in R. This way I will be able to see what you are doing and help you along the way. You will also be creating a repository of all the things you do. You can make posts about everything. Learning specific things in R (project unrelated), and doing things for the project that we will discuss at the beginning of the Fall semester. You can get started now by fiddling around with googling things, and trying stuff out in R. I've placed some helpful starting links in the links page on this website

# What can you do right now by yourself?

It's hard to learn programming when you don't have specific problems that you are trying to solve. Everything just seems abstract.

I wrote an [introductory programming book that introduces R](https://crumplab.github.io/programmingforpsych/), and gives some [concrete problems for you to solve](https://crumplab.github.io/programmingforpsych/programming-challenges-i-learning-the-fundamentals.html). 

To get the hang of journaling and solving the problems to learn programming, my suggestion is that you use this .Rmd file to solve the problems. It would look like this:

# Replace this with problem 4

And keep going. Try to solve the problems with different scripts that provide the same solution. Good luck, Happy coding.
