---
title: "**Aira Contreras' Journal Adventure**"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 2
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```
# Easy Problems

## Problem 4: Prompt and Answer

2019 | Jan | 30 Last compiled: `r Sys.Date()`

##### Prompt: Find the sum of all integers from 1 to 100

##### Answer:
sum function Sol:
```{r}
a<-c()
for(i in 1:100) {
  a<-c(a,i)
}
print(a)
b<-sum(a)
print(b)
```
Loop Sol:
```{r}
c<-0
for(i in 1:100) {
  c<-c+i
}
print(c)
```


## Problem 3: Prompt and Answer

2019 | Jan | 29 Last compiled: `r Sys.Date()`

##### Prompt: Write code that will place the numbers 1 to 100 separately into a variable using for loop. Then, again using the seq function.

##### Answers:

Loop Sol. #1:
```{r}
Alex<-c()

for (i in 1:100) {
  Alex<-c(Alex,i)
  }

print(Alex)
```

Loop Sol. #2:
```{r}
Sol2<-seq(1,100,1)

print(Sol2)
```


## Problem 2: Prompt and Answer

2019 | Jan | 29 Last compiled: `r Sys.Date()`

##### Prompt: Put numbers into variables, do simple math on the variables

##### Answers:
Variable Assingment:
```{r}
A<-5
B<-10
C<-25
D<-30
```
Addition:
```{r}
A+D
```
Subtraction:
```{r}
D-C
```
Multiplication:
```{r}
D*A
```
Division:
```{r}
C/A
```

## Problem 1: Prompt and Answer

2019 | Jan | 29  Last compiled: `r Sys.Date()`

##### Prompt: Do simple math with numbers, addition, subtraction, multiplication, division

##### Answers:
Addition
```{r}
29+20
```
Subtraction
```{r}
29-18
```
Multiplication
```{r}
8*8
```
Division
```{r}
37/5
```

# What can you do right now by yourself?

It's hard to learn programming when you don't have specific problems that you are trying to solve. Everything just seems abstract.

I wrote an [introductory programming book that introduces R](https://crumplab.github.io/programmingforpsych/), and gives some [concrete problems for you to solve](https://crumplab.github.io/programmingforpsych/programming-challenges-i-learning-the-fundamentals.html). 

To get the hang of journaling and solving the problems to learn programming, my suggestion is that you use this .Rmd file to solve the problems. It would look like this:

# Replace this with problem 4

And keep going. Try to solve the problems with different scripts that provide the same solution. Good luck, Happy coding.
