---
title: "**Aira Contreras' Journal Adventure**"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 2
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```
# Harder Problems (1-11)
# Easy Problems (1-21)

## Problem 10: Prompt and Answer

2019 | Feb | 19 Last compiled: `r Sys.Date()`

##### Prompt: Write your own functions to give descriptive statistics for a vector variable storing multiple numbers. Write functions for the following without using R intrinsics: mean, mode, median, range, standard deviation

##### Mean Answer:
```{r}
my_mean<-function(x)
{
  return(sum(x)/length(x))
  
}
t<-c(1:20)
my_mean(t)
```
##### Mode Answer:
```{r}
my_mode<-function(x)
{
 a<-sort(x)
  b<-unique(a)
  maxn<-0
  countn<-0
  for (i in b)
  {
  c<-a[a==i]
  if(length(c)>countn)
    {
    maxn=i
    countn=length(c)
    }
  }
 return(maxn)
}

my_mode(c(1,1,1,10,9,8,8,5,5,5,5))
```
##### Median Answer:
```{r}

my_median<-function(x)
{
  a<-sort(x)
  b<-length(x)
  c<-floor(b/2)
  if(b%%2==0)
  {
    return(mean(c(a[c],a[c+1])))
    
  }
  else
  {
   return(a[c+1])   
  }
}

my_median(c(1,2,3,4,5))
my_median(1:10)
```
##### Range Answer:
```{r}
my_range<-function(x)
{
  sort(x)
  print(c(min(x),max(x)))
}

my_range(c(1,1,1,10,9,8,8,5,5,5,5))
```
##### Standard Deviation Answer:
```{r}

my_sd<-function(x)
{
  avgx<-mean(x)
  sd<-0
  for (i in x)
  {
    sd<-(i-avgx)^2 + sd
  }
  return(sqrt(sd/(length(x)-1)))
}
my_sd(c(-5,1,8,7,2))
```
## Problem 9: Prompt and Answer

2019 | Feb | 19 Last compiled: `r Sys.Date()`

##### Prompt: Generate 100 random numbers within a specific range

##### Answer:

```{r}
#prints all numbers
runif(100, min = 1,max = 100)

#prints integers
floor(runif(100, min = 1,max = 100))

```
## Problem 8: Prompt and Answer

2019 | Feb | 19 Last compiled: `r Sys.Date()`

##### Prompt: Generate 100 random numbers

##### Answer:
```{r}
#prints all numbers
runif(100)

```


## Problem 7: Prompt and Answer

2019 | Feb | 19 Last compiled: `r Sys.Date()`

##### Prompt: List all of the prime numbers from 1 to 1000

##### Answer:
```{r}
prime<-function(x,y)
{
  a<-seq(x,y,1)
  for(i in a)
  {
    c<-"Prime"
    if(i<=1){ c<-"Not Prime"}
    if (i>3)
    {
      
      b<-floor(sqrt(i))
      for(j in 2:b)
      {
        
        if(i%%j==0)
        {
          c<-"Not Prime"
        }
      }
      
    }
    if(c=="Prime")
      {
      print(c(c,i))
      }
  }
}
prime(1,1000)
```

## Problem 6: Prompt and Answer

2019 | Feb | 19 Last compiled: `r Sys.Date()`

##### Prompt: List all of the odd numbers from 1 to 100

##### Answer:

```{r}
seq(1,100,1)

list(1:100)
```


## Problem 5: Prompt and Answer

2019 | Feb | 19 Last compiled: `r Sys.Date()`

##### Prompt: Write a function to find the sum of all integers between any two values

##### Answer:
Sum of All Integers(Random) Sol:
```{r}
rsum<-function(x,y){return(sum(seq(x,y,1)))}

rsum(1,2)
rsum(1,10)
```

## Problem 4: Prompt and Answer

2019 | Jan | 30 Last compiled: `r Sys.Date()`

##### Prompt: Find the sum of all integers from 1 to 100

##### Answer:
sum function Sol:
```{r}
a<-c()
for(i in 1:100) {
  a<-c(a,i)
}
print(a)
b<-sum(a)
print(b)
```
Loop Sol:
```{r}
c<-0
for(i in 1:100) {
  c<-c+i
}
print(c)
```


## Problem 3: Prompt and Answer

2019 | Jan | 29 Last compiled: `r Sys.Date()`

##### Prompt: Write code that will place the numbers 1 to 100 separately into a variable using for loop. Then, again using the seq function.

##### Answers:

Loop Sol. #1:
```{r}
Alex<-c()

for (i in 1:100) {
  Alex<-c(Alex,i)
  }

print(Alex)
```

Loop Sol. #2:
```{r}
Sol2<-seq(1,100,1)

print(Sol2)
```


## Problem 2: Prompt and Answer

2019 | Jan | 29 Last compiled: `r Sys.Date()`

##### Prompt: Put numbers into variables, do simple math on the variables

##### Answers:
Variable Assingment:
```{r}
A<-5
B<-10
C<-25
D<-30
```
Addition:
```{r}
A+D
```
Subtraction:
```{r}
D-C
```
Multiplication:
```{r}
D*A
```
Division:
```{r}
C/A
```

## Problem 1: Prompt and Answer

2019 | Jan | 29  Last compiled: `r Sys.Date()`

##### Prompt: Do simple math with numbers, addition, subtraction, multiplication, division

##### Answers:
Addition
```{r}
29+20
```
Subtraction
```{r}
29-18
```
Multiplication
```{r}
8*8
```
Division
```{r}
37/5
```


