---
title: "Common Inferential Tests"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 3
    #code_folding: hide
---

# Null Distribution of Mean Differences

Assume an alpha criteria of p<.05 for a directional test. What is the critical value for a positive mean difference? In other words, how large must a positive mean difference be in order to occur less than 5% of the time under the null?
Assume an alpha criteria of p<.05 for a non-directional test. What is the critical value for the absolute value of the mean difference. In other words, how large must the absolute value of the mean difference be in order to occur less than 5% of the time under the null?

```{r}
#Normal Distribution M=0, SD=1

#rnorm(10,0,1)

dist<- c()

for (i in 1:10000)
{
  a<-rnorm(10,0,1)
  b<-rnorm(10,0,1)
  
  dist<-c(dist,mean(b)-mean(a))
}

hist(dist)

plot(density(dist))

```

```{r}
testb <- replicate(10000,t.test(rnorm(10,0,1),rnorm(10,0,1))$statistic)
hist(testb)

```

# T-Distribution

For example, what are the probabilities of t(9) >= .5, 1, 1.5, 2, and 2.5? These p-values can be obtained using the qt() function.

Create a simulated t-distribution for the null hypothesis with df=9. Here, the model situation involves taking samples of size n=10 from a normal distribution. The t-value is computed for each sample (sample mean - 0)/SEM. The process is repeated 10,000 times, and each t-value is saved. The resulting 10,000 t-values are the simulated t-distribution.

Using the simulated t-distribution, find the probability of t(9) >= .5, 1, 1.5, 2, and 2.5

Compare the two sets of probabilities to show that the difference is small. What happens to the difference if the simulation is repeated fewer times (e.g., 100) vs. more times (e.g., 100,000)

```{r}
ttest<-function(t,df)
{
  return((1-pt(q=abs(t),df=df))*2)
}
ttest(.5,9)
ttest(1,9)
ttest(1.5,9)
ttest(2,9)
ttest(2.5,9)

```

```{r}
Scores <- rnorm(10, mean = 0, sd = 1)
t.test(Scores,mu=0)
```

# Correlation

Generate the distribution of correlations (Pearson r values) that could be obtained by chance (simulate 10,000 times)

Find the critical value such that the absolute value of the correlation occurs less than 5% of the time by chance.

Find the critical value when the sample-size is increased to 100
```{r}

```

# F-Values

There are three groups of different subjects. The means for each subject in each group are below. Calculate the F-value for the main effect of group.

```{r}

```

# F Simulation

There are three groups of different subjects. The means for each subject in each group are below. Calculate the F-value for the main effect of group.